An inquiry into the influence of parallelism and the choice of random engines on the runtime and results of Stride

### 2018-03-10 assets/src/week4/paper/main.tex
Remove space before footnote

A few of the plots can be seen in \cref{fig:normality}, and for those who would like to see more of them, they can be generated with the script and datafiles found at our website \footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/random\_engines\_stats.py}}.

>>>>

A few of the plots can be seen in \cref{fig:normality}, and for those who would like to see more of them, they can be generated with the script and datafiles found at our website\footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/random\_engines\_stats.py}}.
